---
title: "Project Phase 2"
author: "Connor Thompson, Joseph Wriedt, Hiywot Tulu, Kevin Shin"
date: "April 20, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message = F, warning = F}
library(readr)
library(knitr)
library(ggplot2)
library(dplyr)
```

```{r include = F, message = F, warning = F}
loans = read_csv("http://www.macalester.edu/~dshuman1/data/112/Kiva/loans.csv")
```


## The Dataset

Our data has approximately 93000 cases, each of which represents one loan.  The variables we are considering are as follows:

 - `loan_amount`
 - `sector`
 - `scheduled_payments.count`
 - `funded_yr`
 - `location.country`

## Research Questions

1. Across the most popular sectors, what is the relationship between the number of scheduled payments and the funded amount for the loan?

2. Considering countries with a large quantity of loans, how has the funded amount changed over time? Is this different in different countries?

## Filtering the Dataset

```{r}
e1 <- loans %>% ggplot(aes(x = sector)) + 
  geom_bar() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

e2 <- loans %>% ggplot(aes(x = location.country)) + 
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

grid.arrange(e1,e2,ncols=2)
```



## The First Model

```{r, echo=F, warning=F}
loans %>% filter(sector == c("Food","Agriculture","Retail")) %>% 
  filter(scheduled_payments.count < 500) %>% 
  filter(is.na(scheduled_payments.count) == FALSE) %>% 
  mutate(scheduled_payments.cat = cut(scheduled_payments.count, c(-1,25,100,Inf))) %>% 
  ggplot(aes(y = loan_amount, x = sector, color = factor(scheduled_payments.cat))) +
  geom_boxplot() +
  labs(x = "Sector", y = "Loan Amount")
```

## The Second Model

```{r}
loans %>% filter(location.country == "Peru" | location.country == "Paraguay" |location.country == "Dominican Republic" |location.country == "Jordan" |location.country == "United States" ) %>% 
  filter(!is.na(funded_yr)) %>% 
  ggplot(aes(x = factor(funded_yr), y = loan_amount)) +
    facet_wrap(~location.country)+
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = "Loan Year", y = "Loan Amount")
```

